$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-01 paper/appendix.tex
more on polishing struct

%% Appendix
\section{Structural Congruence}
\label{app:struct}
\begin{nilemma}
  \label{lm:lower-lift}
  The function $lower_i \; P \; uP$ has an inverse $lift_i \; P$ that increments every $\textsc{Var}$ greater than or equal to $i$, such that $lift_i \; (lower_i \; P \; uP) \equiv P$.
\end{nilemma}
\begin{proof}
  By structural induction on \textsc{Process} and \textsc{Var}.
\end{proof}

@@

@@

>>>>

%% Appendix
\section{Structural Congruence}
\label{app:struct}

\begin{nilemma}
  \label{lm:lower-lift}
  The function $lower_i \; P \; uP$ has an inverse $lift_i \; P$ that increments every $\textsc{Var}$ greater than or equal to $i$, such that $lift_i \; (lower_i \; P \; uP) \equiv P$.
\end{nilemma}
\begin{proof}
  By structural induction on \textsc{Process} and \textsc{Var}.
\end{proof}

@@

Structural congruence is a congruent equivalence relation.
As such, rewrites can happen anywhere inside a process, and are closed under reflexivity, symmetry and transitivity as shown by the first row of \autoref{fig:struct-cong1}.
The rest of the rules defines structural congruence under a context $\mathcal{C}[\cdot]$ \cite{Sangio01}, respectively restriction, composition, input and output.

@@

\section{Operational Semantics}
\label{app:os}

\begin{figure}[h]
  \begin{mathpar}
    \datatype
    {n : \N}
    {\Channel_n : \Set}
    \; \textsc{Channel}

    \inferrule
    { }
    {\constr{internal} : \Channel_n}

    \inferrule
    {i : \Var_n}
    {\constr{external} \; i : \Channel_n}

    \datatype
    {i : \Channel_n \\ P \; Q : \Process_n}
    {P \reduce{i} Q : \Set}
    \; \textsc{Reduces}

    \inferrule
    {i \; j : \Var_n \\ P : \Process_{\suc n} \\ Q : \Process_n}
    {\constr{comm} : \comp{\recv{i}P}{\send{i}{j}{Q}} \reduce{\constr{external} \; i} \comp{lower_0 \; (\subst{P}{j}{0})}{Q}}

    \inferrule
    {red : P \reduce{i} P'}
    {\constr{par} \; red : \comp{P}{Q} \reduce{i} \comp{P'}{Q}}

    \inferrule
    {red : P \reduce{i} Q}
    {\constr{res} \; red : \new P \reduce{dec\; i} \new Q}

    \inferrule
    {eq : P = P' \\ red : P' \reduce{i} Q}
    {\constr{struct} \; eq \; red : P \reduce{i} Q}
  \end{mathpar}
  \caption{Operational semantics indexed by the channel over which reduction occurs.}
  \label{fig:reduction1}
  \end{figure}
